---
title: "milestone_3_Meche"
author: "Beau Meche"
date: "April 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(ggplot2)
```

Data: I have 4 sets of census data. My hope was to find literacy and dyslexia statistics relative to the education achievements of the general populations in teh US, but this proves to be a quite scarce commodite even after consultation with the stats department. I am regrouping, but I did find some good sources about schools of choice and public schools by US state (plus Puerto Rico and DC of course). 

Below is a plot I hacked through after hours of fighting for the literacy information. The format was originally encoded by some alpha-numeric jargon that I avoided but have not properly cleaned to date. 
```{r data_imports, echo=FALSE, message=FALSE}
census_2017 <- read_csv(file = "Census_2017_edu_attainment.csv")
census_2016 <- read_csv(file = "Census_edu_attainment_2016.csv")
census_2015 <- read_csv(file = "Census_edu_attainment_2015.csv")
school_type_study <- read_csv(file = "Census_school_type_study_2017.csv")
```

```{r rough_plot, echo=FALSE}
x <- school_type_study %>% select(`GEO.display-label`, HD01_VD05) %>% 
  filter(`GEO.display-label`!= c("Geography","United States")) %>% 
  arrange(desc(as.integer(HD01_VD05))) %>%
  ggplot() + 
  geom_point(aes(x=`GEO.display-label`, y = HD01_VD05, color = "orange"), show.legend = FALSE)  +
  coord_flip() +
  labs(title = "2017 enrollment by state",
       subtitle = "public school counts only",
       caption = "Source: U.S. Census Bureau, 2017 American Community Survey 1-Year Estimates", 
       y = "enrollment counts: excuse the odd arrangement, this is a laborious endeavor", 
       x = "") + 
  theme(axis.text.x = element_text(angle = -90, hjust = 1))
x
```


